How do we copy and paste? The semantic drift of quotations in blogspace

### 2015-03-05 brains-introduction.tex
Change \ref's to named references or remove them (apastyle does not number sections)

The next section (Sec.~\ref{sec:related}) describes our hypotheses along with the relevant state-of-the-art on this psycholinguistic matter.
In Sec.~\ref{sec:protocol}, we detail the empirical protocol and the various assumptions that were made in order to deal with the available empirical material.
Sec.~\ref{sec:results} describes the significant psycholinguistic biases observed during \emph{in vivo} quotation reformulation as well as their epidemiological setting, followed by a discussion and general guidelines for further work in Sec.~\ref{sec:conclusion}.

>>>>

\TB{The next section %(Sec.~\ref{sec:related}) 
describes our hypotheses along with the relevant state-of-the-art on this psycholinguistic matter.
%In Sec.~\ref{sec:protocol}, 
In the section that follows it, 
we detail the empirical protocol and the various assumptions that were made in order to deal with the available empirical material.
%Sec.~\ref{sec:results} 
The results section describes the significant psycholinguistic biases observed during \emph{in vivo} quotation reformulation as well as their epidemiological setting, followed by a discussion and general guidelines for further work in the final section.%Sec.~\ref{sec:conclusion}.
}

### 2015-03-05 brains-protocol.tex
Change \ref's to named references or remove them (apastyle does not number sections)

Manual inspection of this dataset revealed that it contains a significant number of everyday language quotations (such as ``it was much better than I expected'', ``did that just happen'', as well as many simple expletive-based sentences).
Their presence is largely due to random variations around casual expressions, while we are interested in transformations of news-related quotes causally linked to an original, identifiable utterance.
To filter them out, we exclude all quotes having less than 5 words long or lasting more than 80 days %\seb{it is asymmetrical...}
 (as well as quotes not written in English). If an entire cluster still lasts more than 80 days after this screening (because of short-lived but unrelated quotes far apart in time), we also exclude it.
% New filtering: 1051 substitutions out of 6172 mined. 45749 clusters. -- correct text with numbers and for new figures.
We eventually keep 45,749 clusters (out of 71,568; i.e. 63.9\%), containing a total of 127,778 unique quotes (out of 310,457; i.e. 41.2\%) making up $\sim$2.43m occurrences (out of 8.16m, i.e. 29.8\%).\footnote{The significantly larger loss in occurrences indicates that, on average, the clusters we lose contain more occurrences than those we keep, which is expected for everyday language utterances.}
%We contend that the use of the unfiltered dataset would strongly jeopardize results related to linguistic evolution or information diffusion, 
Even if we lose some real event-related utterances which are present in clusters lasting more than 80 days (such as ``the city is tired of me and the organization and I have run our course together''), we check that our approach essentially fulfills its goals by manually coding a random subsample of 100 excluded clusters: a solid 71\% appear to be entirely irrelevant to our analysis (everyday language rather than quotations), and all but one of the remaining clusters were of relevance to the protocol set out below in Sec.~\ref{sec:model}.

>>>>

Manual inspection of this dataset revealed that it contains a significant number of everyday language quotations (such as ``it was much better than I expected'', ``did that just happen'', as well as many simple expletive-based sentences).
Their presence is largely due to random variations around casual expressions, while we are interested in transformations of news-related quotes causally linked to an original, identifiable utterance.
To filter them out, we exclude all quotes having less than 5 words long or lasting more than 80 days %\seb{it is asymmetrical...}
 (as well as quotes not written in English). If an entire cluster still lasts more than 80 days after this screening (because of short-lived but unrelated quotes far apart in time), we also exclude it.
% New filtering: 1051 substitutions out of 6172 mined. 45749 clusters. -- correct text with numbers and for new figures.
We eventually keep 45,749 clusters (out of 71,568; i.e. 63.9\%), containing a total of 127,778 unique quotes (out of 310,457; i.e. 41.2\%) making up $\sim$2.43m occurrences (out of 8.16m, i.e. 29.8\%).\footnote{The significantly larger loss in occurrences indicates that, on average, the clusters we lose contain more occurrences than those we keep, which is expected for everyday language utterances.}
%We contend that the use of the unfiltered dataset would strongly jeopardize results related to linguistic evolution or information diffusion, 
Even if we lose some real event-related utterances which are present in clusters lasting more than 80 days (such as ``the city is tired of me and the organization and I have run our course together''), we check that our approach essentially fulfills its goals by manually coding a random subsample of 100 excluded clusters: a solid 71\% appear to be entirely irrelevant to our analysis (everyday language rather than quotations), and all but one of the remaining clusters were of relevance to the protocol \TB{set out below.}% in Sec.~\ref{sec:model}.
